Response letter on MVAP-D-15-00159R1, \\"Multi-modality Imagery Database for Plant Phenotyping"

### 2015-10-19 datapaper.tex
update

Among many applications of machine vision, plant image analysis has recently began to gain attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
First, MSU-PID is captured using four types of imaging sensors, fluorescence, infrared (IR), RGB color, and depth.
Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
%
%Among many applications of machine vision, plant image analysis has recently begin to gain attentions due to its potential huge impact to plant visual phenotyping, the understanding of plant growth, the quality of crops, and the improvement of the yield.
%Despite its importance, the pack of publicly available research database of plant imagery has substantially hindered the advancement of plant image analysis.
%To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
%First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
%Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
%We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.

>>>>

Among many applications of machine vision, plant image analysis has recently began to gain more attention due to its potential impact on plant visual phenotyping, particularly in understanding plant growth, assessing the quality/performance of crop plants, and improving crop yield.
Despite its importance, the lack of publicly available research databases containing plant imagery has substantially hindered the advancement of plant image analysis.
To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
First, MSU-PID is captured using four types of imaging sensors, fluorescence, infrared (IR), RGB color, and depth.
Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.
%
%Among many applications of machine vision, plant image analysis has recently begin to gain attentions due to its potential huge impact to plant visual phenotyping, the understanding of plant growth, the quality of crops, and the improvement of the yield.
%Despite its importance, the pack of publicly available research database of plant imagery has substantially hindered the advancement of plant image analysis.
%To alleviate this issue, this paper presents a new multi-modality plant imagery database named ``MSU-PID'', with two distinct properties.
%First, MSU-PID is captured using four types of imaging sensors, Fluorescence, infrared (IR), RGB color, and depth.
%Second, the imaging setup and the variety of manual labels allow MSU-PID to be suitable for a diverse set of plant image analysis applications, such as leaf segmentation, leaf counting, leaf alignment, and leaf tracking.
%We provide detailed information on the plants, imaging sensors, calibration, labeling, and baseline performances of this new database.

### 2015-10-19 datapaper_baseline.tex
update

\subsection{Multi-leaf Segmentation and Tracking Framework}
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
We treat all images in $9$ days as a video from first image on the first day to the last image on the last day.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
The scales for fluorescence images and RGB images are different due to the different image resolutions. 
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates for each modality.

@@

In the tracking process, we delete a leaf when it becomes too small.
A new leaf is generated when there is a relatively large portion of the mask that has not been covered by current leaf candidates.
For each frame of the video, we can generate a label image with each leaf being labeled with one color and the tip locations for each estimated leaf.
The labeled color for each leaf in the video remains the same during the tracking process.

@@

Overall, the performance on fluorescence images is better than the performance on RGB images.
This is due to two reasons. 
First, the resolution of RGB images is much lower than that of fluorescence images, which will results in the miss detection of small leaves, and more severe leaf occlusions. 
Second, the label propagation causes some error, which is inevitable with the label homography-based mapping.

>>>>

\subsection{Multi-leaf Segmentation and Tracking Framework}
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
We treat all images in $9$ days as a video from first image on the first day to the last image on the last day.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
The scales for fluorescence images and RGB images are different due to the different image resolutions.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations are scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates for each modality.

@@

In the tracking process, we delete a leaf when it becomes too small.
A new leaf is generated when there is a relatively large portion of the mask that has not been covered by current leaf candidates.
For each frame of the video, we can generate the tip locations for each estimated leaf and a label image with each leaf being labeled with one color.
The labeled color for each leaf in the video remains the same during the tracking process.

@@

Overall, the performance on fluorescence images is better than the performance on RGB images.
This is due to two reasons.
First, the resolution of RGB images is much lower than that of fluorescence images, which will results in more miss detections of small leaves, and more severe leaf occlusions.
Second, the label propagation causes some error, which is inevitable with the label homography-based mapping.

### 2015-10-19 datapapr_labeling.tex
update

\begin{figure*}
\centering
\includegraphics[width=.90\textwidth]{Figures/labeling}\\
\caption{Leaf labeling process, including tip labels and leaf segmentation annotation.}
\label{fig:label}
\end{figure*}

@@

For Arabidopsis images, we labeled $4$ frames per day.
While for bean images, we labeled $7$ frames per day due to the plant's fast and spontaneous leaf movements. 
A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be available to the public.
A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
The results will be automatically saved once a user moves to a previous or next image (``Previous", and ``Next").
For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.

@@

\begin{table*}[t]
\centering
\caption{Human label performance vs. label propagation performance.
$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
The {\it{SBD}} score is averaged over $3$ plants.}
\begin{tabular}{c|c|c|c|c|c|c}
\hline
    & \multicolumn{3}{c|}{fluorescence modality} & \multicolumn{3}{c}{RGB modality}\\ \hline
    & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_1$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
   day$\_3\_$hour$\_23$ & $1$ & $0.808$ & $0.804$ & $1$ & $0.827$ & $0.802$ \\ \hline
   day$\_5\_$hour$\_23$ & $1$ & $0.830$ & $0.836$ & $1$ & $0.871$ & $0.837$ \\ \hline
   day$\_9\_$hour$\_20$ & $1$ & $0.903$ & $0.886$ & $1$ & $0.877$ & $0.789$ \\ \hline
                   average &          $1$ & $0.847$ & $0.842$ & $1$ & $0.858$ & $0.809$ \\ \hline
\end{tabular}
\label{tab:labelError}
\end{table*}

@@

We can make two conclusions from Table~\ref{tab:labelError}.
First, the similarity for both manual annotation and label propagation increases as the plant grows.
This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors larger leaves.
Second, the performance of label propagation is only slightly worse than the performance of human annotations.
Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences.
There are two benefits: $1)$ it decreases the need for manual label; $2)$ labeling is consistent for all four modalities. 
%, which not only saves laborious human labor, but also provides consistent labels for all four modalities.

>>>>

\begin{figure*}
\centering
\includegraphics[width=.90\textwidth]{Figures/labeling}\\
\caption{Leaf annotation process, including leaf tip and leaf segment labels.}
\label{fig:label}
\end{figure*}

@@

For Arabidopsis images, we labeled $4$ frames per day.
While for bean images, we labeled $7$ frames per day due to the plant's fast and spontaneous leaf movements.
A Matlab GUI interface was developed for leaf labeling, as shown in Figure~\ref{fig:label}, which will be released to the public.
A user can open a plant image (``Open") to label the two tips and annotate each leaf segment.
The results will be automatically saved once a user moves to a previous or next image (``Previous", and ``Next").
For consistent annotation of the same leaf over time, we show a number on the center of each leaf indicating the order of labeling from the previous frame.
The users should follow the order to label leaves.

@@

@@

We can make two conclusions from Table~\ref{tab:labelError}.
First, the similarity for both manual annotation and label propagation increases as the plant grows.
This is expected because {\it{SBD}} depends on the overlap ratio between two leaves, which inherently favors large leaves.
Second, the performance of label propagation is only slightly worse than the performance of human annotations.
Therefore, we use label propagation to provide the labels for all four modalities for Arabidopsis sequences.
There are two benefits: $1)$ it decreases the need for manual label; $2)$ labeling is consistent for all four modalities.
%, which not only saves laborious human labor, but also provides consistent labels for all four modalities.

\begin{table}[h]
\centering
\caption{Human label performance vs. label propagation performance.
$L_1$ and $L_2$ are the manual label results from two annotators, and $L_t$ is the propagated results.
The {\it{SBD}} score is averaged over $3$ plants.}
\begin{tabular}{c|c|c|c|c}
\hline
    & \multicolumn{2}{c|}{fluorescence} & \multicolumn{2}{c}{RGB}\\ \hline
    & $L_1$ vs. $L_2$  & $L_1$ vs. $L_t$ & $L_1$ vs. $L_2$ & $L_1$ vs. $L_t$ \\ \hline
   day$\_3$ & $0.808$ & $0.804$ & $0.827$ & $0.802$ \\ \hline
   day$\_5$ & $0.830$ & $0.836$ & $0.871$ & $0.837$ \\ \hline
   day$\_9$ & $0.903$ & $0.886$ & $0.877$ & $0.789$ \\ \hline
    average &   $0.847$ & $0.842$ & $0.858$ & $0.809$ \\ \hline
\end{tabular}
\label{tab:labelError}
\end{table}

### 2015-10-19 list of changes/changes.tex
update

\begin{response}
We have added ``leaf tracking'' to LSC dataset in Table $1$ with a footnote indicating that the temporal data is not available. 
However, the dataset does not include labels which enables leaf alignment task. 
\end{response}

@@

\begin{response}
We have change the corresponding text to ``The provided manual labels allow the evaluation of leaf segmentation and leaf counting. 
Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset''
\end{response}

>>>>

\begin{response}
We have added ``leaf tracking'' to LSC dataset in Table $1$ with a footnote indicating that the temporal data for leaf tracking is not available to the public.
However, the dataset does not include labels which enables leaf alignment task.
\end{response}

@@

\begin{response}
We have change the corresponding text to ``The provided manual labels allow the evaluation of leaf segmentation and leaf counting.
Although it is claimed that they have collected data for leaf tracking, it has not been included in the current LSC dataset.''
\end{response}
